%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}

%---------------------------------------------------------
  \cventrynew
    {Meji Digital, \ \textnormal{\textit{Software Developer | Koregaon Park, Pune}}} % Job title
    {March 2024 - June 2024} % Date(s)
   {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {{\bf Fixed} UI issues to enhance user experience and responsiveness.}
      \item {Integrated {\bf Algolia search functionality} into web applications.}
      \item {{\bf Created, tested, and maintained} Next.js applications using {\bf TypeScript and Tailwind CSS}.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventrynew
    {Azent Overseas Education, \textnormal{\textit{Software Developer | Remote}}} % Organisation
    {Jan 2023 - March 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Azent Admin Panel: {\bf Built} a responsive user interface with React.js, JavaScript, HTML/CSS, and MUI.}
        \item {Component Library: {\bf Established} with {\bf Storybook} and React for component sharing and improved code efficiency.}
        \item {Compass Platform (B2C): {\bf Enhanced} with responsive design and learning paths using React.js and React Router.}
        \item {Scholarship Page: {\bf Created} custom components like {\bf capsule filters}, ensured mobile responsiveness, and integrated with backend APIs.}
        \item {Achievements: Completed major projects demonstrating front-end development, design, and user experience skills.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    {OneTruWeb Software Solutions Pvt Ltd, \ \textnormal{\textit{UI Developer | Remote Freelancing}}} % Organisation
    {Sep 2021 - Sep 2022} % Date(s)
    {
      \begin{cvitems}
        \item {{\bf Developed} the New Skill Sequel Website using React.js, showcasing expertise in modern technologies.}
        \item {{\bf Optimized} WordPress websites for enhanced speed and performance.}
        \item {{\bf Mentored} students with hands-on projects to reinforce theoretical concepts.}
        \item {{\bf Provided training} as a Full Stack Web Development Trainer, equipping individuals with essential development skills.}
        \item {Achievements: Effectively guided students and improved their practical skills through mentorship.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    {Socio ad Pvt. Ltd., \ \textnormal{\textit{Web Developer | On-site}}} % Organisation
    {Jan 2020 - Aug 2021} % Date(s)
    {
      \begin{cvitems}
        \item {{\bf Built} an in-house website using front-end technologies.}
        \item {{\bf Constructed} an internal management portal with front-end and back-end technologies to automate QA and sales team monitoring, improving click-through rates.}
        \item {Collaborated with clients to understand requirements and {\bf created} actionable reports in Tableau, saving 16 hours of manual work per week.}
        \item {Achievements: Enhanced business processes through the development of websites and management portals.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries2}
